---
title: "extractData"
author: "Tobias Granwald"
date: "2025-02-13"
output: html_document
---

# Setup

```{r load useful functions, echo=FALSE}
source("functions/extractQs.R")

extractQs_AC_IDSSR <-  function(responses, nSubj, maxItem, correctResponse){
  Q <- matrix(nrow = nSubj, ncol = 2)
  Q[,1] <- responses
  #remove everything execept response to Attention check
  Q[,1] <- gsub('\\}',"",Q[,1])
  Q[,1] <- gsub('\\{',"",Q[,1])
  Q[,1] <- gsub('\\"',"",Q[,1])
  Q[,1] <- gsub('([.])',"",Q[,1])
  Q[,1] <- gsub('([ ])',"",Q[,1])
  Q[,1] <- gsub("(['])","",Q[,1])
  Q[,1] <- gsub("\\(","",Q[,1])
  Q[,1] <- gsub("\\)","",Q[,1])
  Q[,1] <- gsub("-","",Q[,1])
  Q[,1] <- gsub(paste0('.+,',maxItem,':+.'), "",Q[,1])
  Q[,1] <- gsub(",9A:+.+,+9B:+.+", "",Q[,1])
  Q[,1] <- gsub('([A-z])', "",Q[,1])
  Q[,1] <- gsub(',', "",Q[,1])
  Q[,1] <- gsub(':', "",Q[,1])
  
  # check correct response
  Q[,1] <- gsub(correctResponse, "",Q[,1])
  
  # if correct response Q[,1] should now be empty
  Q[,2] <- ifelse(Q[,1]== "", yes = 0, no = 1)
  
  return(as.numeric(Q[,2]))
}


extractQs_AC_CESD <-  function(responses, nSubj, maxItem, correctResponse){
  Q <- matrix(nrow = nSubj, ncol = 2)
  Q[,1] <- responses
  #remove everything execept response to Attention check
  Q[,1] <- gsub('\\}',"",Q[,1])
  Q[,1] <- gsub('\\{',"",Q[,1])
  Q[,1] <- gsub('\\"',"",Q[,1])
  Q[,1] <- gsub('([.])',"",Q[,1])
  Q[,1] <- gsub('([ ])',"",Q[,1])
  Q[,1] <- gsub("(['])","",Q[,1])
  Q[,1] <- gsub("\\(","",Q[,1])
  Q[,1] <- gsub("\\)","",Q[,1])
  Q[,1] <- gsub("-","",Q[,1])
  Q[,1] <- gsub(paste0('.+,',maxItem,':+.'), "",Q[,1])
  Q[,1] <- gsub(".+day","",Q[,1])
  Q[,1] <- gsub('([A-z])', "",Q[,1])
  Q[,1] <- gsub(',:', "",Q[,1])
  
  # check correct response
  Q[,1] <- gsub(correctResponse, "",Q[,1])
  
  # if correct response Q[,1] should now be empty
  Q[,2] <- ifelse(Q[,1]== "", yes = 0, no = 1)
  
  return(as.numeric(Q[,2]))
}

```


# Load main data

```{r load raw data}
NrowsCorrData <- 1580
fileOfData <- "data/dataRaw/"
errorFiles <- "data/dataRaw/errorData/"
listDataFiles <- list.files(path = paste0(fileOfData), pattern = "priors")
mainDir <- getwd()
subDir <- errorFiles

ifelse(!dir.exists(file.path(mainDir, subDir)), dir.create(file.path(mainDir, subDir)), FALSE)

D <- NULL
errorData <- NULL
temp <- NULL
for (iFiles in listDataFiles) {
  temp <- read.delim(paste0(fileOfData,iFiles), header = T, sep = ",")
  #remove participants with incomplete data (shorter than NrowsCorrData) or who failed to respond in more than 10 trials across the tasks (NrowsCorrData+10*5) 10*5 is because each missed trial gives 5 additional rows. 
  if (nrow(temp)< NrowsCorrData | nrow(temp)> NrowsCorrData+10*5){ 
    file.copy(from = paste0(fileOfData,iFiles), to = paste0(errorFiles,iFiles)) #move to a separate folder for inspection
    # 77 files are moved, 76 with incomplete data, 1 with more than 10 missed trials
  }else {
    #remove participants where rows have NA in trial_index, indicating errors in jsPsych or errors in recording of the data
    if (sum(is.na(temp$trial_index))>0) {
      file.copy(from = paste0(fileOfData,iFiles), to = paste0(errorFiles,iFiles))#move to a separate folder for inspection
      # none removed
    }else{
      D <- rbind(D,temp)
    }
  }
  temp <- NULL
}

listSubjID <- unique(D$subjID)

```


```{r remove participants without valid participant id}

D <- D[!is.na(D$subjID), ]
listSubjID <- unique(D$subjID)

# Only participant with error here had added "...@email.prolific.com" to prolific ID
# As such this step was skipped
#for (i in listSubjID) {
#  if (nchar(i)!=24){
#    print(i)
#    D <- D[D$subjID!=i ,]
#  }
#}
D$subjID <- substr(D$subjID, 1, 24)

# Remove second part of the data with double data
D_issue <- D[D$subjID=="PROLIFIC_ID_ANONOMIZED", ]
D <- D[D$subjID!="PROLIFIC_ID_ANONOMIZED", ]#participant with doubled data removed
D_issue <- D_issue[!duplicated(D_issue$trial_index),] # remove duplicate trials
# remove second oMSTResults
D_issue <- D_issue[1:D_issue[D_issue$category=="oMSTResult" ,]$trial_index[1]+2,]

D<- rbind(D, D_issue)

listSubjID <- unique(D$subjID)
```



```{r remove participants that failed attention checks}
subjMissedCatchTrial2 <- NULL
maxMissedAttentionChecks <- 2

D <- D[!is.na(D$trial_type), ]

for (i in listSubjID) {
  if (maxMissedAttentionChecks<sum(D[D$category=="catchTrial" & D$subjID==i, ]$response == "null")){
    subjMissedCatchTrial2 <- c(subjMissedCatchTrial2, i)
  }
}

if (length(subjMissedCatchTrial2)>0){
  for (i in subjMissedCatchTrial2) {
    D <- D[D$subjID!=i ,]
  }
}

listSubjID <- unique(D$subjID)

length(subjMissedCatchTrial2)
```
1 participant removed due to failing attention checks


## extract data for analysis
```{r}
D$subjID <- substr(D$subjID, 1, 24)
DChoice <- D[D$category=="choice" ,]
#DChoice <- DChoice[DChoice$response!="null", ]
```


```{r remove unused collumns}
DChoiceReduced <- DChoice[,c(5:6,8:10,15:(ncol(DChoice)-7))]
```

### PANAS: Positive Affect

```{r load_PANAS}

#Watson, D., Clark, L. A. & Tellegen, A. Development and Validation of Brief Measures of Positive and Negative Affect: The PANAS Scales. Journal of Personality and Social Psychology 54, 1063–1070 (1988).

# The structure of the raw data is as recorded in a single cell with the following structure:
#"{\"1\":\"4. Quite a Bit\",\"2\":\"1. Very Slightly or Not at All\",\"3\":\"4. Quite a Bit\",\"4\":\"1. Very Slightly or Not at All\",\"5\":\"3. Moderately \",\"6\":\"1. Very Slightly or Not at All\",\"7\":\"1. Very Slightly or Not at All\",\"8\":\"2. A Little\",\"9\":\"4. Quite a Bit\",\"10\":\"5. Extremely\",\"11\":\"3. Moderately \",\"12\":\"5. Extremely\",\"13\":\"2. A Little\",\"14\":\"4. Quite a Bit\",\"15\":\"3. Moderately \",\"16\":\"4. Quite a Bit\",\"17\":\"4. Quite a Bit\",\"18\":\"1. Very Slightly or Not at All\",\"19\":\"4. Quite a Bit\",\"20\":\"2. A Little\",\"AC\":\"1. Choose this option\"}"
#Where AC is the response to the attention check in this scale.

#This function extract the responses:
PANAS_noAC <- extractQs(responses =  D[D$category=="PANAS",]$response, lengthQ = 20, nSubj = length(listSubjID))


PANAS_noAC<- cbind(D[D$category=="PANAS",]$subjID, PANAS_noAC)

#Positive Affect Score Items: 1,3, 5, 9, 10, 12, 14, 16, 17, 19
#Negative Affect Score Items: 2,4,6,7,8,11,13,15,18,20
PA_NA <- matrix(nrow = length(listSubjID), ncol = 2)
for (i in 1:nrow(PANAS_noAC)) {
  PA_NA[i,1] <- sum(c(as.numeric(PANAS_noAC[i,1+2]), #1
                      as.numeric(PANAS_noAC[i,3+2]), #3
                      as.numeric(PANAS_noAC[i,5+2]), #5
                      as.numeric(PANAS_noAC[i,9+2]), #9
                      as.numeric(PANAS_noAC[i,10+2]), #10
                      as.numeric(PANAS_noAC[i,12+2]), #12
                      as.numeric(PANAS_noAC[i,14+2]), #14
                      as.numeric(PANAS_noAC[i,16+2]), #16
                      as.numeric(PANAS_noAC[i,17+2]), #17
                      as.numeric(PANAS_noAC[i,19+2]) #19
                    ))
  PA_NA[i,2] <- sum(c(as.numeric(PANAS_noAC[i,2+2]), #2
                      as.numeric(PANAS_noAC[i,4+2]), #4
                      as.numeric(PANAS_noAC[i,6+2]), #6
                      as.numeric(PANAS_noAC[i,7+2]), #7
                      as.numeric(PANAS_noAC[i,8+2]), #8
                      as.numeric(PANAS_noAC[i,11+2]), #11
                      as.numeric(PANAS_noAC[i,13+2]), #13
                      as.numeric(PANAS_noAC[i,15+2]), #15
                      as.numeric(PANAS_noAC[i,18+2]), #18
                      as.numeric(PANAS_noAC[i,20+2]) #20
                    ))
}
PA_NA <- cbind(D[D$category=="PANAS",]$subjID, PA_NA)
PA_NA <- as.data.frame(PA_NA)
names(PA_NA)<-c("subjID", "PosAffect", "NegAffect")
DChoiceReduced$PosAffect_tot <- NA

for (subj in listSubjID) {
  DChoiceReduced[DChoiceReduced$subjID== subj,]$PosAffect_tot <- PA_NA[PA_NA$subjID==subj,]$PosAffect  
}
 

#write.csv(PA_NA, "data/PANAS_Totals.csv")
```

### STAI-T: Anxiety/depression

```{r load_STAI,echo=FALSE, message=FALSE, warning=FALSE}

#State-Trait Anxiety Inventory for Adults, Form Y-2
# Charles D. Spielberger(1968)

#"{\"1\":\"3. Often\",\"2\":\"1. Almost never\",\"3\":\"4. Almost always\",\"4\":\"1. Almost never\",\"5\":\"1. Almost never\",\"6\":\"3. Often\",\"7\":\"4. Almost always\",\"8\":\"1. Almost never\",\"9\":\"1. Almost never\",\"10\":\"4. Almost always\",\"11\":\"1. Almost never\",\"12\":\"1. Almost never\",\"13\":\"3. Often\",\"14\":\"3. Often\",\"15\":\"1. Almost never\",\"16\":\"4. Almost always\",\"17\":\"1. Almost never\",\"18\":\"1. Almost never\",\"19\":\"3. Often\",\"20\":\"1. Almost never\",\"AC\":\"2. Somewhat\"}"

STAI_T_noAC <- extractQs(responses =  D[D$category== "STAI2",]$response, lengthQ = 20, nSubj = length(listSubjID))

STAI_T_noAC <- cbind(D[D$category=="STAI2",]$subjID, STAI_T_noAC)

#reverse coded 
# 1, 3, 6, 7, 10, 13, 14, 16, 19  
# for these: 4 = 1, 3 = 2, 2 = 3, 1 = 4
staiT <- matrix(nrow = length(listSubjID), ncol = 1)
for (i in 1:nrow(staiT)) {
  staiT[i,1]<- sum(c( (5 - as.numeric(STAI_T_noAC[i,1+2])), #1 R
                      (as.numeric(STAI_T_noAC[i,2+2])), #2 
                      (as.numeric(STAI_T_noAC[i,3+2])), #3
                      (as.numeric(STAI_T_noAC[i,4+2])), #4
                      (as.numeric(STAI_T_noAC[i,5+2])), #5
                      (5 - as.numeric(STAI_T_noAC[i,6+2])), #6 R
                      (5 - as.numeric(STAI_T_noAC[i,7+2])), #7 R
                      (as.numeric(STAI_T_noAC[i,8+2])), #8 
                      (as.numeric(STAI_T_noAC[i,9+2])), #9
                      (5 - as.numeric(STAI_T_noAC[i,10+2])), #10 R
                      (as.numeric(STAI_T_noAC[i,11+2])), #11 
                      (as.numeric(STAI_T_noAC[i,12+2])), #12
                      (5 - as.numeric(STAI_T_noAC[i,13+2])), #13 R
                      (5 - as.numeric(STAI_T_noAC[i,14+2])), #14 R
                      (as.numeric(STAI_T_noAC[i,15+2])), #15 
                      (5 - as.numeric(STAI_T_noAC[i,16+2])), #16 R
                      (as.numeric(STAI_T_noAC[i,17+2])), #17
                      (as.numeric(STAI_T_noAC[i,18+2])), #18
                      (5 - as.numeric(STAI_T_noAC[i,19+2])), #19 R
                      (as.numeric(STAI_T_noAC[i,20+2])) #20 
                      ))
}


staiT <- cbind(D[D$category=="STAI2",]$subjID, staiT)
staiT <- as.data.frame(staiT)
DChoiceReduced$STAIT_tot <- NA

for (subj in listSubjID) {
  DChoiceReduced[DChoiceReduced$subjID== subj,]$STAIT_tot <- staiT[staiT$V1==subj,]$V2
}

names(staiT)<-c("subjID", "staiT")
#write.csv(staiT, "data/STAIT_Totals.csv")

```

### add demographic data

```{r}
demographics <-  read.delim("data/demographics/prolific_export_65ae5edd634d44c4a468fa6e.csv", header = T, sep = ",")


DChoiceReduced$demograph_age <- NA
DChoiceReduced$demograph_sex <- NA
DChoiceReduced$demograph_nationality <- NA
DChoiceReduced$demograph_approvals <- NA
for (subj in listSubjID) {
  if(length(demographics[demographics$Participant.id==subj,]$Age)==1){
    DChoiceReduced[DChoiceReduced$subjID== subj,]$demograph_age <- demographics[demographics$Participant.id==subj,]$Age
    DChoiceReduced[DChoiceReduced$subjID== subj,]$demograph_sex <- demographics[demographics$Participant.id==subj,]$Sex
    DChoiceReduced[DChoiceReduced$subjID== subj,]$demograph_nationality <- demographics[demographics$Participant.id==subj,]$Nationality
    DChoiceReduced[DChoiceReduced$subjID== subj,]$demograph_approvals <- demographics[demographics$Participant.id==subj,]$Total.approvals
    
  }
}
```

## extract attention checks from all questionnaires


```{r anxiety questionnaires_AC}
STAI1_AC <- extractQs_AC(D[D$category=="STAI1",]$response, length(unique(D$subjID)), maxItem = 20, correctResponse = 2)
STAI2_AC <- extractQs_AC(D[D$category=="STAI2",]$response, length(unique(D$subjID)), maxItem = 20, correctResponse = 2)
PSWQ_AC <- extractQs_AC(D[D$category=="PSWQ",]$response, length(unique(D$subjID)), maxItem = 16, correctResponse = 2)
GAD7_AC <- extractQs_AC(D[D$category=="GAD7",]$response, length(unique(D$subjID)), maxItem = 7, correctResponse = 3)
```

```{r motivation_questionnaires_AC}
AMI_AC <- extractQs_AC(D[D$category=="AMI",]$response, length(unique(D$subjID)),maxItem = 18, correctResponse = 3)
SHPS_AC <- extractQs_AC(D[D$category=="SHPS",]$response, length(unique(D$subjID)), maxItem = 14, correctResponse = 3)
BIS_BAS_AC <- extractQs_AC(D[D$category=="BIS_BAS",]$response, length(unique(D$subjID)), maxItem = 24, correctResponse = 1)
```

```{r depression_questionnaires_AC}
PHQ9_AC <- extractQs_AC(D[D$category=="PHQ9",]$response, length(unique(D$subjID)), maxItem = 9, correctResponse = 2)
SDS_AC <- extractQs_AC(D[D$category=="SDS",]$response, length(unique(D$subjID)), maxItem = 20, correctResponse = 2)

PANAS_AC <- extractQs_AC(D[D$category=="PANAS",]$response, length(unique(D$subjID)), maxItem = 20, correctResponse = 1)
RAND36_AC <- extractQs_AC(D[D$category=="RAND36",]$response, length(unique(D$subjID)), maxItem = 36, correctResponse = 4)
```

```{r CESD_questionnaires_AC}
CESD_AC <- extractQs_AC_CESD(D[D$category=="CESD",]$response, length(unique(D$subjID)), maxItem = 20, correctResponse = 2)
```

```{r IDSSR_questionnaires_AC}
IDSSR_AC <- extractQs_AC_IDSSR(D[D$category=="IDSSR",]$response, length(unique(D$subjID)), maxItem = 30, correctResponse = 2)
```

```{r}
full_Q_AC <- cbind(STAI1_AC, STAI2_AC, PSWQ_AC, GAD7_AC, PSWQ_AC,
                   AMI_AC, BIS_BAS_AC, SHPS_AC,
                   PHQ9_AC, SDS_AC, IDSSR_AC, CESD_AC,
                   RAND36_AC, PANAS_AC)

full_Q_AC_sum <- apply(full_Q_AC, 1, sum)

full_Q_AC <- cbind(full_Q_AC,full_Q_AC_sum)
```

### Remove add failed AQ Q to data
```{r}

DChoiceReduced$failed_AC_Q <- 0

for (subj in 1:length(listSubjID)) {
  DChoiceReduced[DChoiceReduced$subjID== listSubjID[subj], ]$failed_AC_Q <- full_Q_AC_sum[subj]
}

```

```{r}
write.csv(full_Q_AC, "data/fail_Q_AC1.csv")
```


# Load Follow-up
```{r load raw data}
NrowsCorrData <- 966
fileOfData <- "data/dataRawFU/"
errorFiles <- "data/dataRawFU/errorData/"
listDataFiles <- list.files(path = paste0(fileOfData), pattern = "priors")
mainDir <- getwd()
subDir <- errorFiles

ifelse(!dir.exists(file.path(mainDir, subDir)), dir.create(file.path(mainDir, subDir)), FALSE)

D2<- NULL
errorData <- NULL
temp <- NULL
for (iFiles in listDataFiles) {
  temp <- read.delim(paste0(fileOfData,iFiles), header = T, sep = ",")
  if (nrow(temp)< NrowsCorrData | nrow(temp)> NrowsCorrData+10*5){
    file.copy(from = paste0(fileOfData,iFiles), to = paste0(errorFiles,iFiles))
    # 14 files are moved, 14 with incomplete data, 0 with more than 10 missed trials
  }else {
    if (sum(is.na(temp$trial_index))>0) {
       file.copy(from = paste0(fileOfData,iFiles), to = paste0(errorFiles,iFiles))
      # none removed
    }else{
      D2 <- rbind(D2,temp)
    }
  }
  temp <- NULL
}

listSubjID2 <- unique(D2$subjID)
```

```{r}

D2 <- D2[!is.na(D2$subjID), ]
listSubjID2 <- unique(D2$subjID)

D2$subjID <- substr(D2$subjID, 1, 24)
# no participant removed for now

for (i in listSubjID2) {
  if (nchar(i)!=24){
    print(i)
    D2 <- D2[D2$subjID!=i ,]
  }
}
# only participant with to wrong length had added "@email.prolific.com", this was removed but not participant

listSubjID2 <- unique(D2$subjID)


#participant with doubled data

# Remove second part of the data with double data
D2_issue <- D2[D2$subjID=="PROLIFIC_ID_ANONOMIZED", ]
D2 <- D2[D2$subjID!="PROLIFIC_ID_ANONOMIZED", ]#participant with doubled data removed
D2_issue <- D2_issue[!duplicated(D2_issue$trial_index),] # remove duplicate trials
# remove second oMSTResults
D2_issue <- D2_issue[1:D2_issue[D2_issue$category=="oMSTResult" ,]$trial_index[1]+2,]

D2<- rbind(D2, D2_issue)


listSubjID2 <- unique(D2$subjID)
```

```{r remove participants that failed attention checks}
subjMissedCatchTrial2 <- NULL
maxMissedAttentionChecks <- 2

D2 <- D2[!is.na(D2$trial_type), ]

for (i in listSubjID2) {
  if (maxMissedAttentionChecks<sum(D2[D2$category=="catchTrial" & D2$subjID==i, ]$response == "null")){
    subjMissedCatchTrial2 <- c(subjMissedCatchTrial2, i)
  }
}

if (length(subjMissedCatchTrial2)>0){
  for (i in subjMissedCatchTrial2) {
    D2 <- D2[D2$subjID!=i ,]
  }
}

listSubjID2 <- unique(D2$subjID)

length(subjMissedCatchTrial2)

```


## extract data for analysis

```{r remove unused collumns}
DChoiceFU <- D2[D2$category=="choice" ,]

DChoiceFU$act <- as.numeric(DChoiceFU$act)

DChoiceReducedFU <- DChoiceFU[,c(5:6,8:10,15:(ncol(DChoiceFU)-7))]
```

### PANAS: Positive Affect

```{r load_PANAS}
PANAS_noAC <- extractQs(responses =  D2[D2$category=="PANAS",]$response, lengthQ = 20, nSubj = length(listSubjID2))

PANAS_noAC<- cbind(D2[D2$category=="PANAS",]$subjID, PANAS_noAC)
#Positive Affect Score Items: 1,3, 5, 9, 10, 12, 14, 16, 17, 19
#Negative Affect Score Items: 2,4,6,7,8,11,13,15,18,20
PA_NA <- matrix(nrow = length(listSubjID2), ncol = 2)
for (i in 1:nrow(PANAS_noAC)) {
  PA_NA[i,1] <- sum(c(as.numeric(PANAS_noAC[i,1+2]), #1
                      as.numeric(PANAS_noAC[i,3+2]), #3
                      as.numeric(PANAS_noAC[i,5+2]), #5
                      as.numeric(PANAS_noAC[i,9+2]), #9
                      as.numeric(PANAS_noAC[i,10+2]), #10
                      as.numeric(PANAS_noAC[i,12+2]), #12
                      as.numeric(PANAS_noAC[i,14+2]), #14
                      as.numeric(PANAS_noAC[i,16+2]), #16
                      as.numeric(PANAS_noAC[i,17+2]), #17
                      as.numeric(PANAS_noAC[i,19+2]) #19
                    ))
  PA_NA[i,2] <- sum(c(as.numeric(PANAS_noAC[i,2+2]), #2
                      as.numeric(PANAS_noAC[i,4+2]), #4
                      as.numeric(PANAS_noAC[i,6+2]), #6
                      as.numeric(PANAS_noAC[i,7+2]), #7
                      as.numeric(PANAS_noAC[i,8+2]), #8
                      as.numeric(PANAS_noAC[i,11+2]), #11
                      as.numeric(PANAS_noAC[i,13+2]), #13
                      as.numeric(PANAS_noAC[i,15+2]), #15
                      as.numeric(PANAS_noAC[i,18+2]), #18
                      as.numeric(PANAS_noAC[i,20+2]) #20
                    ))
}
PA_NA <- cbind(D2[D2$category=="PANAS",]$subjID, PA_NA)
PA_NA <- as.data.frame(PA_NA)
names(PA_NA)<-c("subjID", "PosAffect", "NegAffect")
DChoiceReducedFU$PosAffect_tot <- NA

for (subj in listSubjID2) {
  DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$PosAffect_tot <- PA_NA[PA_NA$subjID==subj,]$PosAffect  
}

#write.csv(PA_NA, "data/PANAS_Totals_FU.csv")
```

### STAI-T: Anxiety/depression

```{r load_STAI,echo=FALSE, message=FALSE, warning=FALSE}

#State-Trait Anxiety Inventory for Adults, Form Y-2
# Charles D. Spielberger(1968)

# the data structure is recorded as follows:
#

STAI_T_noAC <- extractQs(responses =  D2[D2$category== "STAI2",]$response, lengthQ = 20, nSubj = length(listSubjID2))

STAI_T_noAC <- cbind(D2[D2$category=="STAI2",]$subjID, STAI_T_noAC)

#reverse coded 
# 1, 3, 6, 7, 10, 13, 14, 16, 19  
# for these: 4 = 1, 3 = 2, 2 = 3, 1 = 4
staiT <- matrix(nrow = length(listSubjID2), ncol = 1)
for (i in 1:nrow(staiT)) {
  staiT[i,1]<- sum(c( (5 - as.numeric(STAI_T_noAC[i,1+2])), #1 R
                      (as.numeric(STAI_T_noAC[i,2+2])), #2 
                      (as.numeric(STAI_T_noAC[i,3+2])), #3
                      (as.numeric(STAI_T_noAC[i,4+2])), #4
                      (as.numeric(STAI_T_noAC[i,5+2])), #5
                      (5 - as.numeric(STAI_T_noAC[i,6+2])), #6 R
                      (5 - as.numeric(STAI_T_noAC[i,7+2])), #7 R
                      (as.numeric(STAI_T_noAC[i,8+2])), #8 
                      (as.numeric(STAI_T_noAC[i,9+2])), #9
                      (5 - as.numeric(STAI_T_noAC[i,10+2])), #10 R
                      (as.numeric(STAI_T_noAC[i,11+2])), #11 
                      (as.numeric(STAI_T_noAC[i,12+2])), #12
                      (5 - as.numeric(STAI_T_noAC[i,13+2])), #13 R
                      (5 - as.numeric(STAI_T_noAC[i,14+2])), #14 R
                      (as.numeric(STAI_T_noAC[i,15+2])), #15 
                      (5 - as.numeric(STAI_T_noAC[i,16+2])), #16 R
                      (as.numeric(STAI_T_noAC[i,17+2])), #17
                      (as.numeric(STAI_T_noAC[i,18+2])), #18
                      (5 - as.numeric(STAI_T_noAC[i,19+2])), #19 R
                      (as.numeric(STAI_T_noAC[i,20+2])) #20 
                      ))
}


staiT <- cbind(D2[D2$category=="STAI2",]$subjID, staiT)
staiT <- as.data.frame(staiT)
DChoiceReducedFU$STAIT_tot <- NA

for (subj in listSubjID2) {
  DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$STAIT_tot <- staiT[staiT$V1==subj,]$V2
}

names(staiT)<-c("subjID", "staiT")
#write.csv(staiT, "data/STAIT_Totals_FU.csv")
```


### add demographic data

```{r}
demographicsFU <-  read.delim("data/demographics/FU/prolific_export_65c3914e29cea5a205f3d067.csv", header = T, sep = ",")

DChoiceReducedFU$demograph_dateDif <- NA

for (subj in listSubjID2) {
 DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$demograph_dateDif <- (as.Date(demographicsFU[demographicsFU$Participant.id==subj,]$Completed.at))- (as.Date(demographics[demographics$Participant.id==subj,]$Completed.at))
}

max(DChoiceReducedFU[DChoiceReducedFU$trial==1 & DChoiceReducedFU$task=="robber", ]$demograph_dateDif)
min(DChoiceReducedFU[DChoiceReducedFU$trial==1 & DChoiceReducedFU$task=="robber", ]$demograph_dateDif)
mean(DChoiceReducedFU[DChoiceReducedFU$trial==1 & DChoiceReducedFU$task=="robber", ]$demograph_dateDif)
sd(DChoiceReducedFU[DChoiceReducedFU$trial==1 & DChoiceReducedFU$task=="robber", ]$demograph_dateDif)

DChoiceReducedFU$demograph_age <- NA
DChoiceReducedFU$demograph_sex <- NA
DChoiceReducedFU$demograph_nationality <- NA

for (subj in listSubjID2) {
  if(length(demographics[demographics$Participant.id==subj,]$Age)==1){
    DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$demograph_age <- demographics[demographics$Participant.id==subj,]$Age
    DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$demograph_sex <- demographics[demographics$Participant.id==subj,]$Sex
    DChoiceReducedFU[DChoiceReducedFU$subjID== subj,]$demograph_nationality <- demographics[demographics$Participant.id==subj,]$Nationality  
  }
  
}
```

## extract attention checks from all questionnaires


```{r anxiety_questionnaires_FU}
STAI1_AC2 <- extractQs_AC(D2[D2$category=="STAI1",]$response, length(unique(D2$subjID)), maxItem = 20, correctResponse = 2)
STAI2_AC2 <- extractQs_AC(D2[D2$category=="STAI2",]$response, length(unique(D2$subjID)), maxItem = 20, correctResponse = 2)
PSWQ_AC2 <- extractQs_AC(D2[D2$category=="PSWQ",]$response, length(unique(D2$subjID)), maxItem = 16, correctResponse = 2)
GAD7_AC2 <- extractQs_AC(D2[D2$category=="GAD7",]$response, length(unique(D2$subjID)), maxItem = 7, correctResponse = 3)
```

```{r motivation_questionnaires_FU}
AMI_AC2 <- extractQs_AC(D2[D2$category=="AMI",]$response, length(unique(D2$subjID)),maxItem = 18, correctResponse = 3)
SHPS_AC2 <- extractQs_AC(D2[D2$category=="SHPS",]$response, length(unique(D2$subjID)), maxItem = 14, correctResponse = 3)
BIS_BAS_AC2 <- extractQs_AC(D2[D2$category=="BIS_BAS",]$response, length(unique(D2$subjID)), maxItem = 24, correctResponse = 1)
```

```{r depression_questionnaires_FU}
PHQ9_AC2 <- extractQs_AC(D2[D2$category=="PHQ9",]$response, length(unique(D2$subjID)), maxItem = 9, correctResponse = 2)
SDS_AC2 <- extractQs_AC(D2[D2$category=="SDS",]$response, length(unique(D2$subjID)), maxItem = 20, correctResponse = 2)

PANAS_AC2 <- extractQs_AC(D2[D2$category=="PANAS",]$response, length(unique(D2$subjID)), maxItem = 20, correctResponse = 1)
RAND36_AC2 <- extractQs_AC(D2[D2$category=="RAND36",]$response, length(unique(D2$subjID)), maxItem = 36, correctResponse = 4)
```

```{r CESD_questionnaires_FU}
CESD_AC2 <- extractQs_AC_CESD(D2[D2$category=="CESD",]$response, length(unique(D2$subjID)), maxItem = 20, correctResponse = 2)
```

```{r IDSSR_questionnaires_FU}
IDSSR_AC2 <- extractQs_AC_IDSSR(D2[D2$category=="IDSSR",]$response, length(unique(D2$subjID)), maxItem = 30, correctResponse = 2)
```

```{r}
full_Q_AC2 <- cbind(STAI1_AC2, STAI2_AC2, PSWQ_AC2, GAD7_AC2, PSWQ_AC2,
                   AMI_AC2, BIS_BAS_AC2, SHPS_AC2,
                   PHQ9_AC2, SDS_AC2, IDSSR_AC2, CESD_AC2,
                   RAND36_AC2, PANAS_AC2)

full_Q_AC_sum2 <- apply(full_Q_AC2, 1, sum)

full_Q_AC2 <- cbind(full_Q_AC2,full_Q_AC_sum2)
```

### Remove add failed AQ Q to data
```{r}
DChoiceReducedFU$failed_AC_Q <- 0

for (subj in 1:length(listSubjID2)) {
  DChoiceReducedFU[DChoiceReducedFU$subjID== listSubjID2[subj], ]$failed_AC_Q <- full_Q_AC_sum2[subj]
}

```

```{r}
write.csv(full_Q_AC2, "data/fail_Q_AC_FU.csv")
```



# Write extracted data

### Remove prolific ID day 1

```{r}
DChoiceReduced <- cbind("subjID_anon" = rep(0,nrow(DChoiceReduced)), DChoiceReduced)

for (subj in 1:(length(listSubjID))) {
  DChoiceReduced[DChoiceReduced$subjID== listSubjID[subj],]$subjID_anon <- subj
}

DChoiceReduced_anon <- DChoiceReduced[,c(1,3:(ncol(DChoiceReduced)))]

write.csv(DChoiceReduced_anon, file = "data/extractedData.csv", row.names = FALSE)
```


### Remove prolific ID, FU

```{r}
DChoiceReducedFU <- cbind("subjID_anon" = rep(0,nrow(DChoiceReducedFU)), DChoiceReducedFU)

for (subj in 1:(length(listSubjID))) {
  if(length(DChoiceReducedFU[DChoiceReducedFU$subjID== listSubjID[subj],]$subjID_anon)>1){
    DChoiceReducedFU[DChoiceReducedFU$subjID== listSubjID[subj],]$subjID_anon <- subj
  }
}

DChoiceReducedFU_anon <- DChoiceReducedFU[,c(1,3:(ncol(DChoiceReducedFU)))]

write.csv(DChoiceReducedFU_anon, file = "data/extractedData_FU.csv", row.names = FALSE)
```



