---
title: "Regression Models"
author: "Tobias Granwald"
date: "2025-02-11"
output: html_document
---

# Setup

```{r load packages, echo=FALSE, message=FALSE, warning=FALSE}
library("brms")
library("bayesplot")
library("ggplot2")
```

## Load data

```{r load_data, echo=FALSE, message=FALSE,warning=FALSE}
D <- read.delim("data/extractedData.csv", header = TRUE, sep = ",")
```

```{r sort_choice_data,echo=FALSE, message=FALSE, warning=FALSE}
DChoice <- D[D$response!="null", ]

DChoice$act <- as.numeric(DChoice$act)


DChoiceRobber <- DChoice[DChoice$task == "robber" , ]
DChoiceRobber1 <- DChoiceRobber[DChoiceRobber$trial<60, ]
DChoiceRobber2 <- DChoiceRobber[DChoiceRobber$trial>59, ]

DChoiceFactory <- DChoice[DChoice$task == "factory" , ]
DChoiceFactory1 <- DChoiceFactory[DChoiceFactory$trial<60, ]
DChoiceFactory2 <- DChoiceFactory[DChoiceFactory$trial>59, ]

listSubjID <- unique(DChoice$subjID_anon)
```

## Setup models

```{r load_model_parameters, echo=FALSE, message=FALSE, warning=FALSE,}
iterations <- 4500
warmup <- 1000
cores <- parallel::detectCores()
chains <- 7 #cores -1 in on the computer that ran the analysis
seed <- 1337

subDir <- "brmsFiles/"
subDir2 <- "figures/"
mainDir <- getwd()

ifelse(!dir.exists(file.path(mainDir, subDir)), dir.create(file.path(mainDir, subDir)), FALSE) #returns "FALSE" if the folder already exists
ifelse(!dir.exists(file.path(mainDir, subDir2)), dir.create(file.path(mainDir, subDir2)), FALSE) #returns "FALSE" if the folder already exists
```

### Set priors
```{r set priors}
#Model 1
pFit1 <- c(set_prior("normal(0,1.5)", class = "Intercept"),
           set_prior("normal(0,1)", class = "b"),
           set_prior("normal(0,1)", class = "sd"),
           set_prior("lkj(3)", class = "cor"))
#Model 2
pFit2 <- c(set_prior("normal(0,1.5)", class = "Intercept"),
           set_prior("normal(0,1)", class = "b"),
           set_prior("normal(0,1)", class = "sd"),
           set_prior("lkj(3)", class = "cor"))
```


# Robber task, block 1

## Model 1: success last

```{r fit_M1_robber_block1, echo=FALSE, message=T, warning=T, eval=FALSE}
# To ensure that the model doesn't need to be run every time the file is knitted: eval = FALSE and the results are saved for each regression model.

#set up success on the last trial, 1 if success on last trial, 0 if loss or passive choice.
DChoiceRobber1$successLast <- 0
DChoiceRobber1$successLast[2:length(DChoiceRobber1$successLast)] <- DChoiceRobber1$success[1:(length(DChoiceRobber1$success)-1)]

DChoiceRobber1$offerscost <- DChoiceRobber1$offers - DChoiceRobber1$cost 
DChoiceRobber1$stimNo <- as.factor(DChoiceRobber1$stimNo)
DChoiceRobber1$subjID_anon <- as.factor(DChoiceRobber1$subjID_anon)

R1fit1 <- brm(act ~ successLast * offerscost +
                (successLast * offerscost|subjID_anon) +
                (successLast * offerscost|stimNo),
            data = DChoiceRobber1 , 
            family = bernoulli(link = logit),
            prior = pFit1,
            cores = cores-1,
            chains = chains,
            sample_prior = "yes",
            iter = iterations,
            warmup = warmup,
            seed = seed)

save(R1fit1, file = "brmsFiles/R1fit1.rda")
```


```{r load_M1_robber_block1, echo=FALSE}
load("brmsFiles/R1fit1.rda")

R1fit1

H1_R1fit1_success <- hypothesis(R1fit1, "successLast = 0", seed = seed)
H1_R1fit1_offerCost <- hypothesis(R1fit1, "offerscost = 0", seed = seed)
H1_R1fit1_successXofferCost <- hypothesis(R1fit1, "successLast:offerscost = 0", seed = seed)

pp_check(R1fit1)+
  ggtitle("Robber task, Block 1", subtitle = "Model 1") +
  xlab("P(active)")

pp_check(R1fit1, type = "bars", nsamples = 1000) + 
  ggtitle("Robber Task, Block 1", subtitle = "Model 1")
```

### trace plot
```{r traceplot_robber1_M1}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_successLast' = 'Success~Last',
    'b_offerscost' = 'Offer - Cost',
    'b_successLast:offerscost' = 'Success~Last~x~Offer - Cost'
  ), 
  default = label_parsed)

png(filename = "figures/FigS1_tracePlot_R1fit1.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(R1fit1, 
           pars = c("b_Intercept",
                    "b_successLast", 
                    "b_offerscost",
                    "b_successLast:offerscost"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))
dev.off()
```


## Model 2: probwin

```{r fit_M2_robber_block1, echo=FALSE, message=T, warning=T, eval=FALSE}

DChoiceRobber1$trialStim <- 0
for (i in 1:length(listSubjID)) {
  for (j in 1:length(unique(DChoiceRobber1$probWin))) {
      DChoiceRobber1[DChoiceRobber1$subjID_anon==listSubjID[i] & DChoiceRobber1$probWin==unique(DChoiceRobber1$probWin)[j], ]$trialStim <- 
    c(1:length(DChoiceRobber1[DChoiceRobber1$subjID_anon==listSubjID[i] & DChoiceRobber1$probWin==unique(DChoiceRobber1$probWin)[j], ]$trialStim))
  }

}

R1fit2 <- brm(act ~ trialStim * probWin + (trialStim * probWin|subjID_anon),
              data = DChoiceRobber1 , 
              family = bernoulli(link = logit),
              prior = pFit1,
              cores = cores-1,
              chains = chains,
              sample_prior = "yes",
              iter = iterations,
              warmup = warmup,
              seed = seed)

save(R1fit2, file = "brmsFiles/R1fit2.rda")
```


```{r load_M2_robber_block1, echo=FALSE}
load("brmsFiles/R1fit2.rda")
R1fit2
H1_R1fit2_trialStim <- hypothesis(R1fit2, "trialStim  =0", seed = seed)
H1_R1fit2_probWin <- hypothesis(R1fit2, "probWin = 0", seed = seed)
H1_R1fit2_trialStimXprobWin <- hypothesis(R1fit2, "trialStim:probWin = 0", seed = seed)

pp_check(R1fit2)+
  ggtitle("Robber task, Block 1", subtitle = "Model 2") +
  xlab("P(active)")

pp_check(R1fit2, type = "bars", nsamples = 1000) + 
  ggtitle("Robber Task, Block 1", subtitle = "Model 2")

```

### trace plot
```{r traceplot_robber1_M2}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_trialStim' = 'Trial',
    'b_probWin' = 'Success~Prob',
    'b_trialStim:probWin' = 'Trial~x~Success~Prob'
  ), 
  default = label_parsed)

png(filename = "figures/FigS5_tracePlot_R1fit2.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(R1fit2, 
           pars = c("b_Intercept",
                    "b_trialStim", 
                    "b_probWin",
                    "b_trialStim:probWin"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))
dev.off()
```

# Robber task, block 2

## Model 1: success last

```{r fit_M1_robber_block2, echo=FALSE, message=T, warning=T, eval=FALSE}
DChoiceRobber2$successLast <- 0
DChoiceRobber2$successLast[2:length(DChoiceRobber2$successLast)] <- DChoiceRobber2$success[1:(length(DChoiceRobber2$success)-1)]

DChoiceRobber2$offerscost <-DChoiceRobber2$offers - DChoiceRobber2$cost 
DChoiceRobber2$stimNo <- as.factor(DChoiceRobber1$stimNo)
DChoiceRobber2$subjID_anon <- as.factor(DChoiceRobber1$subjID_anon)

R2fit1 <- brm(act ~ successLast * offerscost +
                (successLast * offerscost|subjID_anon) +
                (successLast * offerscost|stimNo),
            data = DChoiceRobber2 , 
            family = bernoulli(link = logit),
            prior = pFit1,
            cores = cores-1,
            chains = chains,
            sample_prior = "yes",
            iter = iterations,
            warmup = warmup,
            seed = seed)

save(R2fit1, file = "brmsFiles/R2fit1.rda")
```


```{r load_M1_robber_block2, echo=FALSE, message=FALSE}
load("brmsFiles/R2fit1.rda")
R2fit1
H1_R2fit1_success <- hypothesis(R2fit1, "successLast = 0", seed = seed)
H1_R2fit1_offerCost <- hypothesis(R2fit1, "offerscost = 0", seed = seed)
H1_R2fit1_successXofferCost <- hypothesis(R2fit1, "successLast:offerscost = 0",
                                          seed = seed)

pp_check(R2fit1)+ ggtitle("Robber Task, Block 2", subtitle = "Model 1") +
  xlab("P(active)")

pp_check(R2fit1, type = "bars", nsamples = 1000) + 
  ggtitle("Robber Task, Block 2", subtitle = "Model 1")
```

### trace plot
```{r traceplot_robber2_M1}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_successLast' = 'Success~Last',
    'b_offerscost' = 'Offer - Cost',
    'b_successLast:offerscost' = 'Success~Last~x~Offer - Cost'
  ), 
  default = label_parsed)

png(filename = "figures/FigS2_tracePlot_R2fit1.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(R2fit1, 
           pars = c("b_Intercept",
                    "b_successLast", 
                    "b_offerscost",
                    "b_successLast:offerscost"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))
dev.off()
```

## Model 2: probwin

```{r fit_M2_robber_block2, echo=FALSE, message=T, warning=T, eval=FALSE}
DChoiceRobber2$trialStim <- 0
for (i in 1:length(listSubjID)) {
  for (j in 1:length(unique(DChoiceRobber1$probWin))) {
      DChoiceRobber2[DChoiceRobber2$subjID_anon==listSubjID[i] & DChoiceRobber2$probWin==unique(DChoiceRobber2$probWin)[j], ]$trialStim <- 
    c(1:length(DChoiceRobber2[DChoiceRobber2$subjID_anon==listSubjID[i] & DChoiceRobber2$probWin==unique(DChoiceRobber2$probWin)[j], ]$trialStim))
  }

}

R2fit2 <- brm(act ~ trialStim * probWin + (trialStim * probWin|subjID_anon),
              data = DChoiceRobber2 , 
              family = bernoulli(link = logit),
              prior = pFit2,
              cores = cores-1,
              chains = chains,
              sample_prior = "yes",
              iter = iterations,
              warmup = warmup,
              control = list(adapt_delta = 0.98),
              seed = seed)

save(R2fit2, file = "brmsFiles/R2fit2.rda")
```


```{r load_M2_robber_block2, echo=FALSE, message=FALSE}
load("brmsFiles/R2fit2.rda")

R2fit2
H1_R2fit2_trialStim <- hypothesis(R2fit2, "trialStim = 0", seed = seed)
H1_R2fit2_probWin <- hypothesis(R2fit2, "probWin = 0", seed = seed)
H1_R2fit2_trialStimXprobWin<- hypothesis(R2fit2, "trialStim:probWin = 0", seed = seed)

pp_check(R2fit2) +
  ggtitle("Robber Task, Block 2", subtitle = "Model 2") + 
  xlab("P(active)")

pp_check(R2fit2, type = "bars", nsamples = 1000) +
  ggtitle("Robber Task, Block 2", subtitle = "Model 2")
```
At delta = 0.8:
"There were 390 divergent transitions after warmup. Increasing adapt_delta above 0.8 may help"

At delta = 0.9:
"There were 101 divergent transitions after warmup. Increasing adapt_delta above 0.9 may help"

At delta = 0.95:
"There were 89 divergent transitions after warmup. Increasing adapt_delta above 0.95 may help" 

Delta set at 0.98.


### trace plot
```{r traceplot_robber2_M2}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_trialStim' = 'Trial',
    'b_probWin' = 'Success~Prob',
    'b_trialStim:probWin' = 'Trial~x~Success~Prob'
  ), 
  default = label_parsed)


png(filename = "figures/FigS6_tracePlot_R2fit2.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(R2fit2, 
           pars = c("b_Intercept",
                    "b_trialStim", 
                    "b_probWin",
                    "b_trialStim:probWin"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))
dev.off()
```


# Factory task, block 1

## Model 1: success last

```{r fit_M1_factory_block1, echo=FALSE, message=T, warning=T, eval=FALSE}
# Set up the parameters used in the model 
DChoiceFactory1$successLast <- 0
DChoiceFactory1$successLast[2:length(DChoiceFactory1$successLast)] <- DChoiceFactory1$success[1:(length(DChoiceFactory1$success)-1)]

DChoiceFactory1$offerscost <-DChoiceFactory1$offers - DChoiceFactory1$cost 
DChoiceFactory1$stimNo <- as.factor(DChoiceFactory1$stimNo)
DChoiceFactory1$subjID_anon <- as.factor(DChoiceFactory1$subjID_anon)

F1fit1 <-   brm(act ~ successLast * offerscost +
                  (successLast * offerscost|subjID_anon) +
                  (successLast * offerscost|stimNo),
            data = DChoiceFactory1 , 
            family = bernoulli(link = logit),
            prior = pFit1,
            cores = cores-1,
            chains = chains,
            sample_prior = "yes",
            iter = iterations,
            warmup = warmup,
            seed = seed)

save(F1fit1, file = "brmsFiles/F1fit1.rda")
```


```{r load_M1_factory_block1, echo=FALSE}
load("brmsFiles/F1fit1.rda")
F1fit1
H1_F1fit1_success <- hypothesis(F1fit1, "successLast = 0", seed = seed)
H1_F1fit1_offerCost <- hypothesis(F1fit1, "offerscost = 0", seed = seed)
H1_F1fit1_successXofferCost <- hypothesis(F1fit1, "successLast:offerscost = 0", 
                                          seed = seed)

pp_check(F1fit1) +
  ggtitle("Factory Task, Block 1", subtitle = "Model 1") +
  xlab("P(active)")
pp_check(F1fit1, type = "bars", nsamples = 1000) + 
  ggtitle("Factory Task, Block 1", subtitle = "Model 1")

```

### trace plot
```{r traceplot_factory1_M1}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_successLast' = 'Success~Last',
    'b_offerscost' = 'Offer - Cost',
    'b_successLast:offerscost' = 'Success~Last~x~Offer - Cost'
  ), 
  default = label_parsed)

png(filename = "figures/FigS3_tracePlot_F1fit1.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(F1fit1, 
           pars = c("b_Intercept",
                    "b_successLast", 
                    "b_offerscost",
                    "b_successLast:offerscost"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))
dev.off()
```

## Model 2: probwin

```{r fit_M2_factory_block1, echo=FALSE, message=T, warning=T, eval=FALSE}
#Set up the 
DChoiceFactory1$trialStim <- 0
for (i in 1:length(listSubjID)) {
  for (j in 1:length(unique(DChoiceFactory1$probWin))) {
      DChoiceFactory1[DChoiceFactory1$subjID_anon==listSubjID[i] & DChoiceFactory1$probWin==unique(DChoiceFactory1$probWin)[j], ]$trialStim <- 
    c(1:length(DChoiceFactory1[DChoiceFactory1$subjID_anon==listSubjID[i] & DChoiceFactory1$probWin==unique(DChoiceFactory1$probWin)[j], ]$trialStim))
  }

}

F1fit2 <- brm(act ~ trialStim * probWin + (trialStim * probWin|subjID_anon),
              data = DChoiceFactory1, 
              family = bernoulli(link = logit),
              prior = pFit2,
              cores = cores-1,
              chains = chains,
              sample_prior = "yes",
              iter = iterations,
              warmup = warmup,
              control = list(adapt_delta = 0.95),
              seed = seed)

save(F1fit2, file = "brmsFiles/F1fit2.rda")
```


```{r load_M2_factory_block1, echo=FALSE,}
load("brmsFiles/F1fit2.rda")

F1fit2
H1_F1fit2_trialStim <- hypothesis(F1fit2, "trialStim = 0", seed = seed)
H1_F1fit2_probWin <- hypothesis(F1fit2, "probWin = 0", seed = seed)
H1_F1fit2_trialStimXprobWin <- hypothesis(F1fit2, "trialStim:probWin = 0", 
                                          seed = seed)
pp_check(F1fit2) +
  ggtitle("Factory Task, Block 1", subtitle = "Model 2") + 
  xlab("P(active)")

pp_check(F1fit2, type = "bars", nsamples = 1000) +
  ggtitle("Factory Task, Block 1", subtitle = "Model 2")
```
At delta = 0.8:
"There were 114 divergent transitions after warmup. Increasing adapt_delta above 0.8 may help"

At delta = 0.9:
"There were 58 divergent transitions after warmup. Increasing adapt_delta above 0.9 may help"

Delta set at 0.95, no divergent transitions.

### trace plot
```{r traceplot_factory1_M2}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_trialStim' = 'Trial',
    'b_probWin' = 'Success~Prob',
    'b_trialStim:probWin' = 'Trial~x~Success~Prob'
  ), 
  default = label_parsed)

png(filename = "figures/FigS7_tracePlot_F1fit2.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(F1fit2, 
           pars = c("b_Intercept",
                    "b_trialStim", 
                    "b_probWin",
                    "b_trialStim:probWin"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))

dev.off()
```


# Factory task, block 2

## Model 1: success last
```{r fit_M1_factory_block2, echo=FALSE, message=T, warning=T, eval=FALSE}
DChoiceFactory2$successLast <- 0
DChoiceFactory2$successLast[2:length(DChoiceFactory2$successLast)] <- DChoiceFactory2$success[1:(length(DChoiceFactory2$success)-1)]

DChoiceFactory2$offerscost <-DChoiceFactory2$offers - DChoiceFactory2$cost 
DChoiceFactory2$stimNo <- as.factor(DChoiceFactory2$stimNo)
DChoiceFactory2$subjID_anon <- as.factor(DChoiceFactory2$subjID_anon)

F2fit1 <- brm(act ~ successLast * offerscost +
                (successLast * offerscost|subjID_anon) +
                (successLast * offerscost|stimNo),
              data = DChoiceFactory2 , 
              family = bernoulli(link = logit),
              prior = pFit1,
              cores = cores-1,
              chains = chains,
              sample_prior = "yes",
              iter = iterations,
              warmup = warmup,
              seed = seed)

save(F2fit1, file = "brmsFiles/F2fit1.rda")
```


```{r load_M1_factory_block2, echo=FALSE}
load("brmsFiles/F2fit1.rda")

F2fit1
H1_F2fit1_success <- hypothesis(F2fit1, "successLast = 0", seed = seed)
H1_F2fit1_offerCost <- hypothesis(F2fit1, "offerscost = 0", seed = seed)
H1_F2fit1_successXofferCost <- hypothesis(F2fit1, "successLast:offerscost = 0", 
                                          seed = seed)
pp_check(F2fit1)+
  ggtitle("Factory Task, Block 2", subtitle = "Model 1") +
  xlab("P(active)")
pp_check(F2fit1, type = "bars", nsamples = 1000) +
  ggtitle("Factory Task, Block 2", subtitle = "Model 1")
```

### trace plot
```{r traceplot_factory2_M1}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_successLast' = 'Success~Last',
    'b_offerscost' = 'Offer - Cost',
    'b_successLast:offerscost' = 'Success~Last~x~Offer - Cost'
  ), 
  default = label_parsed)

png(filename = "figures/FigS4_tracePlot_F2fit1.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(F2fit1, 
           pars = c("b_Intercept",
                    "b_successLast", 
                    "b_offerscost",
                    "b_successLast:offerscost"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))

dev.off()
```


## Model 2: probwin

```{r fit_M2_factory_block2, echo=FALSE, message=T, warning=T, eval=FALSE}
DChoiceFactory2$trialStim <- 0
for (i in 1:length(listSubjID)) {
  for (j in 1:length(unique(DChoiceFactory2$probWin))) {
      DChoiceFactory2[DChoiceFactory2$subjID_anon==listSubjID[i] & DChoiceFactory2$probWin==unique(DChoiceFactory2$probWin)[j], ]$trialStim <- 
    c(1:length(DChoiceFactory2[DChoiceFactory2$subjID_anon==listSubjID[i] & DChoiceFactory2$probWin==unique(DChoiceFactory2$probWin)[j], ]$trialStim))
  }

}

F2fit2 <- brm(act ~ trialStim * probWin + (trialStim * probWin|subjID_anon),
              data = DChoiceFactory2 , 
              family = bernoulli(link = logit),
              prior = pFit1,
              cores = cores-1,
              chains = chains,
              sample_prior = "yes",
              iter = iterations,
              warmup = warmup,
              control = list(adapt_delta = 0.95),
              seed = seed)

save(F2fit2, file = "brmsFiles/F2fit2.rda")
```


```{r load_M2_factory_block2, echo=FALSE}
load("brmsFiles/F2fit2.rda")

F2fit2
H1_F2fit2_trialStim <- hypothesis(F2fit2, "trialStim = 0", seed = seed)
H1_F2fit2_probWin <-hypothesis(F2fit2, "probWin = 0", seed = seed)
H1_F2fit2_trialStimXprobWin <- hypothesis(F2fit2, "trialStim:probWin = 0", seed = seed)

pp_check(F2fit2) +
  ggtitle("Factory Task, Block 2", subtitle = "Model 2") + 
  xlab("P(active)")
pp_check(F2fit1, type = "bars", nsamples = 1000) +
  ggtitle("Factory Task, Block 2", subtitle = "Model 2")
```
At delta = 0.8
"There were 514 divergent transitions after warmup. Increasing adapt_delta above 0.8 may help. See http://mc-stan.org/misc/warnings.html#divergent-transitions-after-warmup"

At delta = 0.95
"There were 3 divergent transitions after warmup. Increasing adapt_delta above 0.95 may help. See http://mc-stan.org/misc/warnings.html#divergent-transitions-after-warmup"

This was considered fine, and used in the analysis.

### trace plot
```{r traceplot_factory1_M2}
my_labeller_one <- as_labeller(x = c(
    'b_Intercept' = 'Intercept',
    'b_trialStim' = 'Trial',
    'b_probWin' = 'Success~Prob',
    'b_trialStim:probWin' = 'Trial~x~Success~Prob'
  ), 
  default = label_parsed)

png(filename = "figures/FigS8_tracePlot_F2fit2.png", 
    width = ((700*2))/3, height = 1400/3)

mcmc_trace(F2fit2, 
           pars = c("b_Intercept",
                    "b_trialStim", 
                    "b_probWin",
                    "b_trialStim:probWin"),
           facet_args = list(nrow = 2, labeller = my_labeller_one),
           window = c(0, iterations-warmup))

dev.off()
```


# Response to reviewers' comments


```{r function to plot model fit against data, echo = FALSE}
plot_heatMapFit <- function(model, ndraws, data_choice, plotTitle, colRamp = 60, filename){
  y_rep <- posterior_predict(model, ndraws = ndraws)
  
  y_rep_subj <- matrix(nrow = length(unique(data_choice$subjID_anon)), ncol = 60)
  dist_binom <- matrix(nrow = 60, ncol = length(unique(data_choice$subjID_anon)))
  temp_sample_yrep <- NULL
  sumAct_subj <- NULL
  for (subj in unique(data_choice$subjID_anon)) {
    temp_sample_yrep <- y_rep[, data_choice$subjID_anon == subj]
    y_rep_subj[subj,] <- apply(temp_sample_yrep, 2, mean)
    dist_binom[,subj] <- dbinom(c(1:60), size = 60, mean(y_rep_subj[subj,]))
    
    sumAct_subj[subj] <- sum(data_choice[data_choice$subjID_anon == subj, ]$act)
  }
  
  dist_binomSort <- dist_binom[,order(sumAct_subj)]

  png(filename = filename, 
      width = ((700*2))/3, height = 1500)
  par(mar = c(4,4,2,2))
  
  image(dist_binomSort, ylab = "", 
        xlab = "N trials active chosen", 
        yaxt = "n", xaxt = "n",
        main = plotTitle, cex.lab = 1.7, cex.main = 2,
        col = hcl.colors(colRamp, "YlOrRd", rev = TRUE))
  mtext(side = 2, text = "Subjects, sorted by N trials active chosen", 
        line = 1, cex = 1.7)
  axis(1, at= c(1:60/60), labels = c(1:60), cex.lab = 3)
  axis(2, at= c(1/279, 1), labels = c(1, 279), cex.lab = 3)
  sorted_act<- sort(sumAct_subj)
  y_subj <- seq(from = 0, to = 1, length.out = 279)
  for (subj in 1:length(sumAct_subj)) {

    points(x = (sorted_act[subj])/60, y = y_subj[subj], pch = 20, cex = .4)
    #points(x = (sorted_act[subj])/60, y = y_subj[subj], pch = 1, cex = .01, col = "white")
  }
  #abline(h= 1)
  points(rep(1,colRamp),
         (1:colRamp)/100,
         col= hcl.colors(colRamp, "YlOrRd", rev = TRUE),
         pch = 15, cex = 3)
  
  text(x = 0.95, y =(1)/100,"0" )
  text(x = 0.94, y =(colRamp)/100,labels = round(max(dist_binomSort),2))
  text(x = 0.94, y = (colRamp/2)/100, labels = "Density", srt = 90, cex = 1.5)
  lines(x = c(0.9, 0.9), y = c(0,(colRamp+0.7)/100))
  lines(x = c(1, 0.9), y = c((colRamp+0.7)/100,(colRamp+0.7)/100))
  
  dev.off()
}
```


## Robber 1

### M1

```{r}

offerCost_drawPrior<- prior_draws(R1fit1, variable = "b_offercost")

offerCost_drawPost <- as_draws_df(R1fit1)

par(mfrow=c(2,1), mar=c(0,4,1,1), oma=c(4,0,0,0)) 
plot(density(offerCost_drawPost$b_offerscost), col= "tomato", lwd = 2, xlim= c(-3.5,3.5),
     ylim= c(10, 170),
     main = "",
     xaxt = "n", 
     xlab = "n",
     ylab = "",
     )
abline(v = mean(offerCost_drawPrior$b_offercost), lty = 3)
text(-3.8, 3, "//", cex=1.5,xpd = NA, srt = 145)

par(mar=c(0,4,0,1))

plot(density(offerCost_drawPrior$b_offercost), xlim = c(-3.5, 3.5), col= "dodgerblue", lwd = 2, ylim = c(0, 5), main = "",
     ylab = "")
abline(v = mean(offerCost_drawPrior$b_offercost), lty = 3)
lines(density(offerCost_drawPost$b_offerscost), col= "tomato",lwd = 2)
legend(x = 1.5,y = 3, col = c("dodgerblue", "tomato"), lty = 1,lwd = 3, legend = c("prior", "posterior") )

mtext("Offer - Cost", side = 1, outer = TRUE, line=2,
        cex = 1, at = c(0.54) , family = "Arial", font = 2)
mtext("Density", side = 2, outer = TRUE, line=-1,
        cex = 1, family = "Arial", font = 2)

```

```{r}

success_drawPrior<- prior_draws(R1fit1, variable = "b_successLast")

success_drawPost <- as_draws_df(R1fit1)

par(mar=c(0,4,1,1), oma=c(4,0,0,0)) 
plot(density(success_drawPrior$b_successLast), xlim = c(-3.5, 3.5), col= "dodgerblue", lwd = 2, ylim = c(0, 5), main = "",
     ylab = "",
     xlab = "")
abline(v = mean(success_drawPrior$b_successLast), lty = 3)
  lines(density(success_drawPost$b_successLast), col= "tomato",lwd = 2)
legend(x = 1.5,y = 2, col = c("dodgerblue", "tomato"), lty = 1,lwd = 3, legend = c("prior", "posterior") )

mtext("Success last", side = 1, outer = TRUE, line=2,
        cex = 1, at = c(0.54) , family = "Arial", font = 2)
mtext("Density", side = 2, outer = TRUE, line=-1,
        cex = 1, family = "Arial", font = 2)

```


```{r}
plot_heatMapFit(model = R1fit1, ndraws = 3000,
                data_choice = DChoiceRobber1, 
                plotTitle = "Robber block 1, Model 1",
                colRamp = 60,
                filename = "figures/modelfit_R1_M1.png")
```

### M2
```{r}
plot_heatMapFit(model = R1fit2, ndraws = 3000,
                data_choice = DChoiceRobber1, 
                plotTitle = "Robber block 1, Model 2",
                colRamp = 60,
                filename = "figures/modelfit_R1_M2.png")
```

## Robber 2

### M1
```{r}
plot_heatMapFit(model = R2fit1, ndraws = 3000,
                data_choice = DChoiceRobber2, 
                plotTitle = "Robber block 2, Model 1",
                colRamp = 60,
                filename = "figures/modelfit_R2_M1.png")
```


### M2
```{r}
plot_heatMapFit(model = R2fit2, ndraws = 3000,
                data_choice = DChoiceRobber2, 
                plotTitle = "Robber block 2, Model 2",
                colRamp = 60,
                filename = "figures/modelfit_R2_M2.png")
```

## Factory 1

### M1
```{r}
plot_heatMapFit(model = F1fit1, ndraws = 3000,
                data_choice = DChoiceFactory1, 
                plotTitle = "Factory block 1, Model 1",
                colRamp = 60,
                filename = "figures/modelfit_F1_M1.png")
```

### M2
```{r}
plot_heatMapFit(model = F1fit2, ndraws = 3000,
                data_choice = DChoiceFactory1, 
                plotTitle = "Factory block 1, Model 2",
                colRamp = 60,
                filename = "figures/modelfit_F1_M2.png")
```

## Factory 2

### M1
```{r}
plot_heatMapFit(model = F2fit1, ndraws = 3000,
                data_choice = DChoiceFactory2, 
                plotTitle = "Factory block 2, Model 1",
                colRamp = 60,
                filename = "figures/modelfit_F2_M1.png")
```

### M2
```{r}
plot_heatMapFit(model = F2fit2, ndraws = 3000,
                data_choice = DChoiceFactory2, 
                plotTitle = "Factory block 2, Model 2",
                colRamp = 60,
                filename = "figures/modelfit_F2_M2.png")
```
